---
title: "Introduction"
---

```{r}
#| echo: false
source("_common.R")
knitr::opts_chunk$set(echo = FALSE)

```

```{r }
#| include: false
# load libraries and functions-----------------------------------------------
source(file.path("..", "scripts", "Librerias.R"))
source(file.path("..", "scripts", "Funciones.R"))

```

PREGVAL is a population-based cohort of pregnancies in the Region of Valencia, a region in south-eastern Spain with a population of 5 million.

The PREGVAL cohort was constructed using a hierarchical approach that integrated data from different electronic health registries to create a comprehensive dataset on pregnancy outcomes. First, records with available gestational age were prioritised, allowing an accurate assessment of pregnancy duration. Subsequently, for records without this information, gestational age was imputed using the median gestational age derived from the type of end of pregnancy and source of the data.

The process started with the Metabolic Disease Registry (MDR), which captured live births. Additional insights were sourced from the Perinatal Mortality Registry (PMR), enriching the dataset with more live births and comprehensive records of stillbirths, essential for a complete picture of perinatal mortality.

The dataset was further enhanced by the inclusion of data from the Congenital Anomalies Registry (CONG), which provides details of both live births and stillbirths affected by congenital anomalies. The Minimum Basic Data Set (MBDS) contributed significantly by including records of elective, spontaneous and unknown abortions, in addition to regular live births and stillbirths.

The Electronic Obstetric Sheet (EOS) registry provided additional data on live births, stillbirths and spontaneous abortions. In cases where gestational age was not initially recorded, further data were extracted from the MBDS using alternative codes, the Adverse Event Database (AED), and Specialist Care Examinations (CEX). The Primary Care Visits (PCV) registry provided additional insight, particularly valuable for pregnancies without detailed gestational age records.

For cases without recorded gestational age, the cohort methodology was to impute the median gestational age for each type of outcome across the respective databases. This approach ensured the robustness and comprehensiveness of the dataset, allowing detailed analysis of pregnancy outcomes under different scenarios.

<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>
