---
title: "Quality Check: Processing CEX. Empadronados"
---

```{r}
#| echo: false
source("_common.R")
knitr::opts_chunk$set(echo = FALSE)

```

```{r }
#| include: false
# load libraries and functions-----------------------------------------------
source(file.path("..", "scripts", "Librerias.R"))
source(file.path("..", "scripts", "Funciones.R"))

```

```{css, echo = FALSE}
.output {
max-height: 500px;
overflow-y: scroll;
}

```

## Input

```{r}
# read empadronados
sips_empadronados <- readRDS(file.path("..", "PREGVAL", "Results", "sips", 
                           "sips_empadronados.RDS"))

```

```{r}
# select the input-----------------------------------------------------------
table_name <- "cex.csv"
cex <- fread2(file.path("..", "QC_project", "datos", "Pregval", table_name), na.strings = "",
  # read code columns as character    
  colClasses = list(character = 3:16)) |> 
  filter(sip %in% sips_empadronados)

# CONSIGN
# load table-----------------------------------------------------------------
# cex <- fread2(file.path("datos", "Consign", "cex.csv"))

# PREGVAL 2009-2012
# load table-----------------------------------------------------------------
# cex <- fread2(file.path("datos", "Pregval", "cex_2009_2012_clean.csv"))

# PREGVAL 2013-2017
# load table-----------------------------------------------------------------
# cex <- fread2(file.path("datos", "Pregval", "cex_2013_2017_clean.csv"))

# PREGVAL 2018-2021
# load table-----------------------------------------------------------------
# cex <- fread2(file.path("datos", "Pregval", "cex_2018_2021_clean.csv"))

```

The table to be analysed is **`r table_name`**.

```{r}
# set the study variables----------------------------------------------------
start_of_study_period <- ymd("2009-01-01")
end_of_study_period   <- ymd("2021-12-31")

# PREGVAL 2009-2012----------------------------------------------------------
if (str_detect(table_name, "2009_2012") == TRUE){
  start_of_study_period <- ymd("2009-01-01")
  end_of_study_period <- ymd("2012-12-31")
}

if (str_detect(table_name, "2013_2017") == TRUE){
# PREGVAL 2013-2017----------------------------------------------------------
  start_of_study_period <- ymd("2013-01-01")
  end_of_study_period <- ymd("2017-12-31")
}

if (str_detect(table_name, "2018_2021") == TRUE){
# PREGVAL 2018-2021----------------------------------------------------------
  start_of_study_period <- ymd("2018-01-01")
  end_of_study_period <- ymd("2021-12-31")
}

```

```{r}
# load names-----------------------------------------------------------------
vid_names <- readRDS(file.path("..", "EHDEN", "Results", "vid_catalogue",
                               "vid_names.RDS"))

```

```{r}
# load population------------------------------------------------------------
# sips_clean <- readRDS(file.path("..", "PREGVAL", "Results", 
#                                 "sips", "sips_clean.RDS"))
# sips_total <- sips_clean

sips_total <- sips_empadronados


```

## Check variables

```{r}
# capture the names of the instance table------------------------------------
instance_names <- cex |> 
  names() 

```

The variables extracted from CEX are: `r colorize(knitr::combine_words(instance_names), "blue")`.

```{r}
# check mandatory variables--------------------------------------------------
missing_mandatory_vars <- vid_names$cex_mandatory_names |> 
  keep(~. %nin% instance_names)

missing_mandatory_print <- "All mandatory vars are present"  

if (missing_mandatory_vars |> length() > 0) missing_mandatory_print <-
  glue("{knitr::combine_words(missing_mandatory_vars)} are missing")
      
color_mandatory_check <- if_else(missing_mandatory_vars |> length() > 0,
                                 "red", "green")

```

### Check mandatory vars 

`r colorize(missing_mandatory_print, color_mandatory_check)`.

```{r}
# check variables in full names----------------------------------------------
missing_full_vars <- vid_names$cex_all_names |> 
  keep(~. %nin% instance_names)

if(missing_full_vars |> length() > 0){
missing_full_print <- glue("{knitr::combine_words(missing_full_vars)} were not extracted")
}else{
missing_full_print <- "All possible vars are present"
}

color_full_check <- if_else(missing_full_vars |> length() > 0,
                                 "red", "green")

```

### Check all vars 

`r colorize(missing_full_print, color_full_check)`.

### Completeness

In @fig-cexcompleteness is shown the percentage of non-missing values for each variable. Non-mandatory variables are shown at the bottom of the figure.

```{r}
#| warning: false
# clean and fix----------------------------------------------------------
# manipulate unknown values to NA (0_00, -1, -2, etc.)
vector_of_nas <- c("", "0:00", "****", "0:DESCONOCIDA", "-1", "-2")

```


```{r}
# function to check completeness---------------------------------------------
check_completeness <- function(table, var){
if (as_string(ensym(var)) %nin% names(cex)) {
  return(lst(missing_obs = nrow(cex),
           complete_pct = 0,
           print_missing = "0%",
           color_missing = "red"
  ))
  }
total_obs <- table |> nrow() 
missing_obs <-  table |> filter(is.na({{var}})) |> nrow()
complete_pct <- 100 * ((total_obs - missing_obs)/total_obs) |> 
  round(3)
  
print_missing <- glue("{complete_pct}%")
color_missing <- if_else(missing_obs == 0, "green", "orange")
return(lst(missing_obs,
           complete_pct,
           print_missing,
           color_missing
            ))
}

```


```{r}
# apply the function to each var---------------------------------------------
miss_fecha_consulta       <- check_completeness(cex, fecha_consulta)
miss_especialidad_cod          <- check_completeness(cex, especialidad_cod)
miss_especialidad_desc         <- check_completeness(cex, especialidad_desc)
miss_d1_cod             <- check_completeness(cex, d1_cod)
miss_d1_desc            <- check_completeness(cex, d1_desc)
miss_d2_cod             <- check_completeness(cex, d2_cod)
miss_d2_desc            <- check_completeness(cex, d2_desc)
miss_d3_cod             <- check_completeness(cex, d3_cod)
miss_d3_desc            <- check_completeness(cex, d3_desc)
miss_d4_cod             <- check_completeness(cex, d4_cod)
miss_d4_desc            <- check_completeness(cex, d4_desc)

miss_tipo_codigo1          <- check_completeness(cex, tipo_codigo1)
miss_tipo_codigo2          <- check_completeness(cex, tipo_codigo2)
miss_tipo_codigo3          <- check_completeness(cex, tipo_codigo3)
miss_tipo_codigo4          <- check_completeness(cex, tipo_codigo4)

```

```{r}
# ensamble the missings------------------------------------------------------
tibble_missings <- data.frame(var = vid_names$cex_all_names,
                pct = map_dbl(vid_names$cex_all_names, 
                ~check_completeness(cex, var = !!sym(.x))$complete_pct),
                complete = map_chr(vid_names$cex_all_names, 
                ~check_completeness(cex, var = !!sym(.x))$print_missing)) |> 
  as_tibble() |> 
  mutate(var = fct_rev(fct_inorder(var))) |> 
  mutate(type = if_else(var %in% vid_names$cex_mandatory_names, 
                        "#9473d8", "#f2cce4"))

```

<br>

```{r}
#| label: fig-cexcompleteness
#| fig-cap: "Variables completeness"
# plot the missings----------------------------------------------------------

ggplot(tibble_missings, aes(y = var, x = pct)) +
  geom_col(aes(fill = type)) + 
  geom_text(aes(label = complete),
            colour = "black",
            position = position_nudge(7),
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Variable") +
  scale_x_continuous(name = "Completeness", 
                     breaks = c(0, 25, 50, 75, 100),
                     labels = scales::comma) +
  theme(axis.text = element_text(size = 20))
  
```

<br>

## Check content

```{r}
# total number of rows-------------------------------------------------------
total_cex_observations <- cex |> nrow()
  
```

The **CEX** table has a total of **n = `r total_cex_observations |> pretty2()` observations**.

### Population

```{r}
# total distinct individuals-------------------------------------------------
distinct_sips_n <- cex |> distinct(sip) |> nrow() 
distinct_sips <- distinct_sips_n |> pretty2()
total_sips <- sips_total |> length() |> pretty2()
# individuals in population--------------------------------------------------
sips_in_pop_n <- cex |> 
  distinct(sip) |> 
  filter(sip %in% sips_total) |> 
  nrow() 
sips_in_pop <- sips_in_pop_n |> pretty2()

color_in_pop <- if_else(sips_in_pop < distinct_sips, "red", "green")

print_pop <- if_else(color_in_pop == "red", 
             glue("From these, there are {distinct_sips_n - sips_in_pop_n} individuals that are not included in the target population"),
             glue("All the individuals are included in the target population"))

percent_sips <- (sips_in_pop_n /  sips_total |> length()) * 100

print_percent_sips <- glue("{percent_sips |> round(2)}%")

```

- In **CEX** table there are `r colorize(distinct_sips, "blue")` distinct individuals. `r colorize(print_pop, color_in_pop)`. Therefore, there are `r colorize(sips_in_pop, color_in_pop)` individuals included in the target population out of the `r colorize(total_sips, "purple")` total individuals in the cohort. These represents `r colorize(print_percent_sips, "blue")` of the total.

```{r}
# number of individuals per year---------------------------------------------
cex_sips_per_year <- cex |> 
  filter(sip %in% sips_total) |> 
  group_by(year = year(fecha_consulta)) |> 
  distinct(sip) |> 
  count(year) |> 
  ungroup()

```

- The @tbl-sipsperyear shows the number of individuals per year of the study period.

<br>

```{r}
#| label: tbl-sipsperyear
#| tbl-cap-location: top
#| tbl-cap: "Number of individuals per year of calculation"
# create table of number of individuals per year-----------------------------
cex_sips_per_year |> 
  gt(id = "sipsperyear") |>  # need to name the table to apply CSS
  cols_label(year = "Year of visit",
             n = "Count of distinct individuals") |> 
  cols_align(
  align = c("center"),
  columns = everything()
  ) |> 
  tab_style(
    style = list(
      cell_fill(color = "#9473d8"),
      cell_text(color = "white", align = "center", weight = "bold")
    ),
    locations = cells_column_labels()) |> 
    opt_row_striping( row_striping = TRUE) |> 
  opt_css(
    css = "
    #sipsperyear tr:hover {
    background-color: #f2cce4;
    }
    ")

```

<br>

### Date of the visit

```{r}
# check if the date of the visit is inside the study period------------------
date_of_visit_print <- "All visits are inside the study period"  
color_of_visit_print <- "green"

n_visits_ok <- cex |> mutate(date_of_visit_ok = between(fecha_consulta, 
                      start_of_study_period, end_of_study_period)) |> 
  summarise(n = 100 * mean(date_of_visit_ok, na.rm = TRUE)) |> 
  pull()

if (n_visits_ok < 100){

n_visits_before <- cex |> 
  mutate(date_of_visit_before = fecha_consulta < start_of_study_period) |> 
  summarise(n = 100 * mean(date_of_visit_before, na.rm = TRUE)) |> 
  pull() |> round(2)

n_visits_after <- cex |> 
  mutate(date_of_visit_after = fecha_consulta > end_of_study_period) |> 
  summarise(n = 100 * mean(date_of_visit_after, na.rm = TRUE)) |> 
  pull() |> round(2)

# n_visits_na <- cex |> mutate(date_of_visit_na = is.na(fecha_consulta)) |> 
#   summarise(n = 100 * mean(date_of_visit_na)) |> pull()

date_of_visit_print <- glue("There are visits outside the study period. From the non-missing visits: \n
                            * **{n_visits_ok |> round(2)}%** are inside the study period. \n
                            * **{n_visits_before}%** occurred before the start of the study period. \n
                            * **{n_visits_after}%** occurred after the end of the study period") 
color_of_visit_print <- "red"
}      

min_date <- cex |> filter(!is.na(fecha_consulta)) |> 
summarise(min(fecha_consulta)) |> pull()
max_date <- cex |> filter(!is.na(fecha_consulta)) |> 
summarise(max(fecha_consulta)) |> pull()

```

The variable *fecha_consulta* is missing in **`r miss_fecha_consulta$missing_obs` observations**, so it is `r colorize(miss_fecha_consulta$print_missing, miss_fecha_consulta$color_missing)` complete. The minimum and maximum date are ***`r min_date`*** and ***`r max_date`*** respectively. @tbl-fechacons shows the number of visits per year of *fecha_consulta*.

`r colorize(date_of_visit_print, color_of_visit_print)`.

<br>

```{r}
#| label: tbl-fechacons
#| tbl-cap-location: top
#| tbl-cap: "Number of visits each year of calculation"
# create table of number of visits per year-----------------------------
cex |> 
  count(year = year(fecha_consulta)) |> 
  gt(id = "fechacons") |>  # need to name the table to apply CSS
  cols_label(year = "Year of the visit",
             n = "Count") |> 
  cols_align(
  align = c("left"),
  columns = everything()
  ) |> 
  tab_style(
    style = list(
      cell_fill(color = "#9473d8"),
      cell_text(color = "white", align = "left", weight = "bold")
    ),
    locations = cells_column_labels()) |> 
    opt_row_striping( row_striping = TRUE) |> 
  opt_css(
    css = "
    #fechacons tr:hover {
    background-color: #f2cce4;
    }
    ")

```

<br>

```{r}
# check month and year of fecha_consulta-------------------------------------
cex_month_year_visit_date <- cex |> 
  count(month = month(fecha_consulta, 
                      label = TRUE,
                      abbr = FALSE,
                      locale = "EN"), 
        year = year(fecha_consulta),
        name = "n_month_year") |> 
  arrange(year, month)

cex_month_year_visit_date_min <- cex_month_year_visit_date |> 
  filter(n_month_year == min(n_month_year))
cex_month_year_visit_date_max <- cex_month_year_visit_date |> 
  filter(n_month_year == max(n_month_year))

print_month_year_visit_date_min <- glue(
  "{cex_month_year_visit_date_min |> pull(month)} {cex_month_year_visit_date_min |> pull(year)} with n = {cex_month_year_visit_date_min |> pull(n_month_year)}" )

print_month_year_visit_date_max <- glue(
  "{cex_month_year_visit_date_max |> pull(month)} {cex_month_year_visit_date_max |> pull(year)} with n = {cex_month_year_visit_date_max |> pull(n_month_year)}" )

```

The month and year with less visits was `r colorize(print_month_year_visit_date_min, "blue")` and the month and year with more visits was `r colorize(print_month_year_visit_date_max, "purple")`.

In @fig-cexvisityear, @fig-cexvisitmonth, and @fig-cexvisitday are presented the frequencies of years, months, and days of the visits respectively.

<br>

```{r}
#| label: fig-cexvisityear
#| fig-cap: "Visit year"
# plot year of fecha_consulta------------------------------------------------
cex_year_visit <- cex |> 
  count(year_visit = year(fecha_consulta), name = "n_year")

ggplot(cex_year_visit) +
  geom_col(aes(x = year_visit, y = n_year), fill = "#9473d8") +
  xlab("Visit year") +
  scale_y_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text = element_text(size = 20))

```

<br>

```{r}
#| label: fig-cexvisitmonth
#| fig-cap: "Visit month"
# plot month of fecha_consulta-----------------------------------------------
cex_month_visit <- cex |> 
  count(month_visit = month(fecha_consulta, label = TRUE,
                                locale = "EN"), name = "n_month")

ggplot(cex_month_visit) +
  geom_col(aes(x = month_visit, y = n_month), fill = "#9473d8") +
  xlab("Visit month") +
  scale_y_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text = element_text(size = 20))

```

<br>

```{r}
#| label: fig-cexvisitday
#| fig-cap: "Visit day"
# plot day of fecha_consulta-------------------------------------------------
cex_day_visit <- cex |> 
  count(day_visit = day(fecha_consulta), name = "n_day")

ggplot(cex_day_visit) +
  geom_col(aes(x = day_visit, y = n_day), fill = "#9473d8") +
  scale_x_continuous(name = "Visit day", 
                   breaks = 1:31, labels = 1:31) +
  scale_y_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text = element_text(size = 20))

```

<br>

### Visit service

The variable *especialidad_desc* is missing in **`r miss_especialidad_desc$missing_obs` observations**, so it is `r colorize(miss_especialidad_desc$print_missing, miss_especialidad_desc$color_missing)` complete. @tbl-visit shows all the services used in the specialist visits arranged by alphabetic order. @fig-cexesp shows the count of the utilization of each visit service. Finally, @fig-cexespyear shows the count of visits for the 10 most used services per year.

<br>

```{r}
#| label: tbl-visit
#| tbl-cap-location: top
#| tbl-cap: "Healths services used in the specialist visits"
# create table of especialidad_desc------------------------------------------

cex |> 
  tabyl(especialidad_desc) |>
  adorn_pct_formatting(digits = 2) |> 
  gt(id = "serv") |>  # need to name the table to apply CSS
  cols_label(especialidad_desc = "Service",
             n = "Count",
             percent = "Percentage") |> 
  cols_align(
  align = c("left"),
  columns = everything()
  ) |> 
  tab_style(
    style = list(
      cell_fill(color = "#9473d8"),
      cell_text(color = "white", align = "left", weight = "bold")
    ),
    locations = cells_column_labels()) |> 
    opt_row_striping( row_striping = TRUE) |>
  tab_options(
    container.height = "700px"
  ) |>
  opt_css(
    css = "
    #serv tr:hover {
    background-color: #f2cce4;
    }
    ")

```

<br>

```{r}
#| label: fig-cexesp
#| fig-cap: "specialist visit services"

# plot especialidad_desc-----------------------------------------------------
x_pos <- nrow(cex) / 10

cex |>
  mutate(especialidad_desc = fct_lump_n(fct_infreq(especialidad_desc), 
                             n = 10, other_level = "OTROS") |> fct_rev()) |> 
  count(especialidad_desc) |>
  mutate(n_all = sum(n)) |> 
  mutate(percent = glue("{round(100 * n / n_all, 1)}%")) |> 
  # make colour for na
  mutate(fill_color = if_else(is.na(especialidad_desc),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = especialidad_desc, x = n)) +
  geom_col(aes(fill = fill_color)) + 
  geom_text(aes(label = percent),
            colour = "black",
            size = 7,
            fontface = "bold",
            x = x_pos
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Health Service") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text = element_text(size = 20))

```

<br>

```{r}
#| label: fig-cexespyear
#| fig-cap: "Most used specialist visit services per year"
# plot especialidad_desc per year--------------------------------------------

xpos2 <- x_pos/(cex |> distinct(year(fecha_consulta)) |> nrow())

cex |>
  mutate(especialidad_desc = fct_lump_n(fct_infreq(especialidad_desc),
                      n = 10, other_level = "OTROS") |> fct_rev()) |>
  mutate(year = year(fecha_consulta)) |>
  count(year, especialidad_desc) |>
  group_by(year) |> 
  mutate(n_year = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_year, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(especialidad_desc),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = especialidad_desc, x = n)) +
  geom_col(aes(fill = fill_color)) +
  facet_wrap(~year, ncol = 4) +
  geom_text(aes(label = percent),
            colour = "black",
            size = 7,
            fontface = "bold",
            x = xpos2
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Health Service") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(
    axis.text.y = element_text(size = 20),
    axis.text.x = element_text(size = 20, angle = 90))

```

<br>
 
### Diagnoses codes: d1_cod 

The variable *d1_cod* is missing in **`r miss_d1_cod$missing_obs` observations**, so it is `r colorize(miss_d1_cod$print_missing, miss_d1_cod$color_missing)` complete. @fig-cexcode1 shows the most employed diagnoses codes. Finally, @fig-cexcode1year shows the count of the 10 most employed codes per year.

<br>

```{r}
#| label: fig-cexcode1
#| fig-cap: "Diagnosis codes (d1_cod) used in specialist visits"
# plot d1_cod-----------------------------------------------------------
x_pos <- nrow(cex)/10

cex |>
  mutate(d1_cod = fct_lump_n(fct_infreq(d1_cod), n = 10, 
                                   other_level = "OTROS") |> fct_rev()) |>
  count(d1_cod) |> 
  mutate(n_all = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_all, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(d1_cod),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = d1_cod, x = n)) +
  geom_col(aes(fill = fill_color)) +
  geom_text(aes(label = percent),
            colour = "black",
            size = 7,
            x = x_pos,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Diagnosis codes") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text = element_text(size = 20))

```


<br>

```{r}
#| label: fig-cexcode1year
#| fig-cap: "Diagnosis codes (d1_cod) used in specialist visits per year"
# plot d1_cod per year-------------------------------------------------------

cex |>
  mutate(d1_cod = fct_lump_n(fct_infreq(d1_cod), n = 10, 
                                   other_level = "OTROS") |> fct_rev()) |>
  mutate(year = year(fecha_consulta)) |>
  count(year, d1_cod) |>
  group_by(year) |> 
  mutate(n_year = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_year, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(d1_cod),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = d1_cod, x = n)) +
  geom_col(aes(fill = fill_color)) +
  facet_wrap(~year, ncol = 4) +
  geom_text_repel(aes(label = percent),
            colour = "black",
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Diagnosis Codes") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text.x = element_text(size = 20, angle = 90))

```

<br>

### Diagnoses codes: d2_cod 

The variable *d2_cod* is missing in **`r miss_d2_cod$missing_obs` observations**, so it is `r colorize(miss_d2_cod$print_missing, miss_d2_cod$color_missing)` complete. @fig-cexcode1 shows the most employed diagnoses codes. Finally, @fig-cexcode1year shows the count of the 10 most employed codes per year.

<br>

```{r}
#| label: fig-cexcode2
#| fig-cap: "Diagnosis codes (d2_cod) used in specialist visits"
# plot d2_cod-----------------------------------------------------------
x_pos <- nrow(cex)/10

cex |>
  mutate(d2_cod = fct_lump_n(fct_infreq(d2_cod), n = 10, 
                                   other_level = "OTROS") |> fct_rev()) |>
  count(d2_cod) |> 
  mutate(n_all = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_all, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(d2_cod),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = d2_cod, x = n)) +
  geom_col(aes(fill = fill_color)) +
  geom_text(aes(label = percent),
            colour = "black",
            size = 7,
            x = x_pos,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Diagnosis codes") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text = element_text(size = 20))

```

<br>

```{r}
#| label: fig-cexcode2year
#| fig-cap: "Diagnosis codes (d2_cod) used in specialist visits per year"
# plot d2_cod per year-------------------------------------------------------

cex |>
  mutate(d2_cod = fct_lump_n(fct_infreq(d2_cod), n = 10, ties.method = "first", 
                                   other_level = "OTROS") |> fct_rev()) |>
  mutate(year = year(fecha_consulta)) |>
  count(year, d2_cod) |>
  group_by(year) |> 
  mutate(n_year = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_year, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(d2_cod),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = d2_cod, x = n)) +
  geom_col(aes(fill = fill_color)) +
  facet_wrap(~year, ncol = 4) +
  geom_text_repel(aes(label = percent),
            colour = "black",
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Diagnosis Codes") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text.x = element_text(size = 20, angle = 90))

```

<br>

### Diagnoses codes: d3_cod 

The variable *d3_cod* is missing in **`r miss_d3_cod$missing_obs` observations**, so it is `r colorize(miss_d3_cod$print_missing, miss_d3_cod$color_missing)` complete. @fig-cexcode1 shows the most employed diagnoses codes. Finally, @fig-cexcode1year shows the count of the 10 most employed codes per year.

<br>

```{r}
#| label: fig-cexcode3
#| fig-cap: "Diagnosis codes (d3_cod) used in specialist visits"
# plot d3_cod-----------------------------------------------------------
x_pos <- nrow(cex)/10

cex |>
  mutate(d3_cod = fct_lump_n(fct_infreq(d3_cod), n = 10, 
                                   other_level = "OTROS") |> fct_rev()) |>
  count(d3_cod) |> 
  mutate(n_all = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_all, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(d3_cod),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = d3_cod, x = n)) +
  geom_col(aes(fill = fill_color)) +
  geom_text(aes(label = percent),
            colour = "black",
            size = 7,
            x = x_pos,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Diagnosis codes") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text = element_text(size = 20))

```


<br>

```{r}
#| label: fig-cexcode3year
#| fig-cap: "Diagnosis codes (d3_cod) used in specialist visits per year"
# plot d3_cod per year-------------------------------------------------------

cex |>
  mutate(d3_cod = fct_lump_n(fct_infreq(d3_cod), n = 10, ties.method = "first", 
                                   other_level = "OTROS") |> fct_rev()) |>
  mutate(year = year(fecha_consulta)) |>
  count(year, d3_cod) |>
  group_by(year) |> 
  mutate(n_year = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_year, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(d3_cod),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = d3_cod, x = n)) +
  geom_col(aes(fill = fill_color)) +
  facet_wrap(~year, ncol = 4) +
  geom_text_repel(aes(label = percent),
            colour = "black",
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Diagnosis Codes") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text.x = element_text(size = 20, angle = 90))

```

<br>

### Diagnoses codes: d4_cod 

The variable *d4_cod* is missing in **`r miss_d4_cod$missing_obs` observations**, so it is `r colorize(miss_d4_cod$print_missing, miss_d4_cod$color_missing)` complete. @fig-cexcode1 shows the most employed diagnoses codes. Finally, @fig-cexcode1year shows the count of the 10 most employed codes per year.

<br>

```{r}
#| label: fig-cexcode4
#| fig-cap: "Diagnosis codes (d4_cod) used in specialist visits"
# plot d4_cod-----------------------------------------------------------
x_pos <- nrow(cex)/10

cex |>
  mutate(d4_cod = fct_lump_n(fct_infreq(d4_cod), n = 10, 
                                   other_level = "OTROS") |> fct_rev()) |>
  count(d4_cod) |> 
  mutate(n_all = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_all, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(d4_cod),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = d4_cod, x = n)) +
  geom_col(aes(fill = fill_color)) +
  geom_text(aes(label = percent),
            colour = "black",
            size = 7,
            x = x_pos,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Diagnosis codes") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text = element_text(size = 20))

```


<br>

```{r}
#| label: fig-cexcode4year
#| fig-cap: "Diagnosis codes (d4_cod) used in specialist visits per year"
# plot d4_cod per year-------------------------------------------------------

cex |>
  mutate(d4_cod = fct_lump_n(fct_infreq(d4_cod), n = 10, ties.method = "first", 
                                   other_level = "OTROS") |> fct_rev()) |>
  mutate(year = year(fecha_consulta)) |>
  count(year, d4_cod) |>
  group_by(year) |> 
  mutate(n_year = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_year, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(d4_cod),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = d4_cod, x = n)) +
  geom_col(aes(fill = fill_color)) +
  facet_wrap(~year, ncol = 4) +
  geom_text_repel(aes(label = percent),
            colour = "black",
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Diagnosis Codes") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text.x = element_text(size = 20, angle = 90))

```

<br>

### Code vocabulary: tipo_codigo1

The variable *tipo_codigo1* is missing in **`r miss_tipo_codigo1$missing_obs` observations**, so it is `r colorize(miss_tipo_codigo1$print_missing, miss_tipo_codigo1$color_missing)` complete. @fig-cextipo1 shows the count of the utilization of each visit service. Finally, @fig-cextipo1year shows the count of visits for the 10 most used services per year.

<br>

```{r}
#| label: fig-cextipo1
#| fig-cap: "Code (d1_cod) vocabularies used in specialist visits"
# plot tipo_codigo1----------------------------------------------------------
cex |>
  tabyl(tipo_codigo1) |>
  adorn_pct_formatting() |> 
  mutate(tipo_codigo1 = fct_reorder(tipo_codigo1, n)) |> 
  # make colour for na
  mutate(fill_color = if_else(is.na(tipo_codigo1),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = tipo_codigo1, x = n)) +
  geom_col(aes(fill = fill_color)) + 
  geom_text(aes(label = percent),
            colour = "black",
            position = position_nudge(100),
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Code Vocabulary") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text.y = element_text(size = 20))

```


<br>

```{r}
#| label: fig-cextipo1year
#| fig-cap: "Code (d1_cod) vocabularies used in specialist visits per year"
# plot tipo_codigo1 per year--------------------------------------------------

cex |>
  mutate(tipo_codigo1 = fct_infreq(tipo_codigo1) |> fct_rev()) |>
  mutate(year = year(fecha_consulta)) |>
  count(year, tipo_codigo1) |>
  group_by(year) |> 
  mutate(n_year = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_year, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(tipo_codigo1),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = tipo_codigo1, x = n)) +
  geom_col(aes(fill = fill_color)) +
  facet_wrap(~year, ncol = 4) +
  geom_text_repel(aes(label = percent),
            colour = "black",
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Code Vocabulary") +
  scale_x_continuous(name = "Count", labels = scales::label_comma()) +
  theme(axis.text.x = element_text(size = 20, angle = 90))

```

<br>

### Code vocabulary: tipo_codigo2

The variable *tipo_codigo2* is missing in **`r miss_tipo_codigo2$missing_obs` observations**, so it is `r colorize(miss_tipo_codigo2$print_missing, miss_tipo_codigo2$color_missing)` complete. @fig-cextipo2 shows the count of the utilization of each visit service. Finally, @fig-cextipo2year shows the count of visits for the 10 most used services per year.

<br>

```{r}
#| label: fig-cextipo2
#| fig-cap: "Code (d2_cod) vocabularies used in specialist visits"
# plot tipo_codigo2----------------------------------------------------------
cex |>
  tabyl(tipo_codigo2) |>
  adorn_pct_formatting() |> 
  mutate(tipo_codigo2 = fct_reorder(tipo_codigo2, n)) |> 
  # make colour for na
  mutate(fill_color = if_else(is.na(tipo_codigo2),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = tipo_codigo2, x = n)) +
  geom_col(aes(fill = fill_color)) + 
  geom_text(aes(label = percent),
            colour = "black",
            position = position_nudge(100),
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Code Vocabulary") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text.y = element_text(size = 20))

```


<br>

```{r}
#| label: fig-cextipo2year
#| fig-cap: "Code (d2_cod) vocabularies used in specialist visits per year"
# plot tipo_codigo2 per year--------------------------------------------------

cex |>
  mutate(tipo_codigo2 = fct_infreq(tipo_codigo2) |> fct_rev()) |>
  mutate(year = year(fecha_consulta)) |>
  count(year, tipo_codigo2) |>
  group_by(year) |> 
  mutate(n_year = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_year, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(tipo_codigo2),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = tipo_codigo2, x = n)) +
  geom_col(aes(fill = fill_color)) +
  facet_wrap(~year, ncol = 4) +
  geom_text_repel(aes(label = percent),
            colour = "black",
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Code Vocabulary") +
  scale_x_continuous(name = "Count", labels = scales::label_comma()) +
  theme(axis.text.x = element_text(size = 20, angle = 90))

```

<br>

### Code vocabulary: tipo_codigo3

The variable *tipo_codigo3* is missing in **`r miss_tipo_codigo3$missing_obs` observations**, so it is `r colorize(miss_tipo_codigo3$print_missing, miss_tipo_codigo3$color_missing)` complete. @fig-cextipo3 shows the count of the utilization of each visit service. Finally, @fig-cextipo3year shows the count of visits for the 10 most used services per year.

<br>

```{r}
#| label: fig-cextipo3
#| fig-cap: "Code (d3_cod) vocabularies used in specialist visits"
# plot tipo_codigo3----------------------------------------------------------
cex |>
  tabyl(tipo_codigo3) |>
  adorn_pct_formatting() |> 
  mutate(tipo_codigo3 = fct_reorder(tipo_codigo3, n)) |> 
  # make colour for na
  mutate(fill_color = if_else(is.na(tipo_codigo3),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = tipo_codigo3, x = n)) +
  geom_col(aes(fill = fill_color)) + 
  geom_text(aes(label = percent),
            colour = "black",
            position = position_nudge(100),
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Code Vocabulary") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text.y = element_text(size = 20))

```

<br>

```{r}
#| label: fig-cextipo3year
#| fig-cap: "Code (d3_cod) vocabularies used in specialist visits per year"
# plot tipo_codigo3 per year--------------------------------------------------

cex |>
  mutate(tipo_codigo3 = fct_infreq(tipo_codigo3) |> fct_rev()) |>
  mutate(year = year(fecha_consulta)) |>
  count(year, tipo_codigo3) |>
  group_by(year) |> 
  mutate(n_year = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_year, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(tipo_codigo3),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = tipo_codigo3, x = n)) +
  geom_col(aes(fill = fill_color)) +
  facet_wrap(~year, ncol = 4) +
  geom_text_repel(aes(label = percent),
            colour = "black",
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Code Vocabulary") +
  scale_x_continuous(name = "Count", labels = scales::label_comma()) +
  theme(axis.text.x = element_text(size = 20, angle = 90))

```

<br>

### Code vocabulary: tipo_codigo4

The variable *tipo_codigo4* is missing in **`r miss_tipo_codigo4$missing_obs` observations**, so it is `r colorize(miss_tipo_codigo4$print_missing, miss_tipo_codigo4$color_missing)` complete. @fig-cextipo4 shows the count of the utilization of each visit service. Finally, @fig-cextipo4year shows the count of visits for the 10 most used services per year.

<br>

```{r}
#| label: fig-cextipo4
#| fig-cap: "Code (d4_cod) vocabularies used in specialist visits"
# plot tipo_codigo4----------------------------------------------------------
cex |>
  tabyl(tipo_codigo4) |>
  adorn_pct_formatting() |> 
  mutate(tipo_codigo4 = fct_reorder(tipo_codigo4, n)) |> 
  # make colour for na
  mutate(fill_color = if_else(is.na(tipo_codigo4),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = tipo_codigo4, x = n)) +
  geom_col(aes(fill = fill_color)) + 
  geom_text(aes(label = percent),
            colour = "black",
            position = position_nudge(100),
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Code Vocabulary") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text.y = element_text(size = 20))

```


<br>

```{r}
#| label: fig-cextipo4year
#| fig-cap: "Code (d4_cod) vocabularies used in specialist visits per year"
# plot tipo_codigo4 per year--------------------------------------------------

cex |>
  mutate(tipo_codigo4 = fct_infreq(tipo_codigo4) |> fct_rev()) |>
  mutate(year = year(fecha_consulta)) |>
  count(year, tipo_codigo4) |>
  group_by(year) |> 
  mutate(n_year = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_year, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(tipo_codigo4),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = tipo_codigo4, x = n)) +
  geom_col(aes(fill = fill_color)) +
  facet_wrap(~year, ncol = 4) +
  geom_text_repel(aes(label = percent),
            colour = "black",
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Code Vocabulary") +
  scale_x_continuous(name = "Count", labels = scales::label_comma()) +
  theme(axis.text.x = element_text(size = 20, angle = 90))

```

<br>

<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>
