---
title: "Quality Check: Processing AED. Empadronados"
author: "Francisco Sanchez-Saez"
date: "last-modified" 
editor: source
format:
  html:
    toc: true
    toc-location: left
    theme: cerulean
    css: style.css
    embed-resources: true
    number-sections: true
    output-file: "PREGVAL_AED_empadronados.html" 
---

```{r}
#| echo: false
source("_common.R")
knitr::opts_chunk$set(echo = FALSE)

```

```{r }
#| include: false
# load libraries and functions-----------------------------------------------
source(file.path("..", "scripts", "Librerias.R"))
source(file.path("..", "scripts", "Funciones.R"))

```

```{css, echo = FALSE}
.output {
max-height: 500px;
overflow-y: scroll;
}

```

## Input

```{r}
# read empadronados
sips_empadronados <- readRDS(file.path("..", "PREGVAL", "Results", "sips", 
                           "sips_empadronados.RDS"))

```

```{r}
# select the input-----------------------------------------------------------
table_name <- "aed.csv"

aed <- fread2(file.path("..", "QC_project", "datos", "Pregval", table_name),
               na.strings = "",
  # read code columns as character    
  colClasses = list(character = 10:15)) |> 
  filter(sip %in% sips_empadronados)

# CONSIGN
# load table-----------------------------------------------------------------
# aed <- fread2(file.path("datos", "Consign", "aed.csv"))

# PREGVAL 2009-2012
# load table-----------------------------------------------------------------
# aed <- fread2(file.path("datos", "Pregval", "aed_2009_2012_clean.csv"))

# PREGVAL 2013-2017
# load table-----------------------------------------------------------------
# aed <- fread2(file.path("datos", "Pregval", "aed_2013_2017_clean.csv"))

# PREGVAL 2018-2021
# load table-----------------------------------------------------------------
# aed <- fread2(file.path("datos", "Pregval", "aed_2018_2021_clean.csv"))

```

The table to be analysed is **`r table_name`**.

```{r}
# set the study variables----------------------------------------------------
start_of_study_period <- ymd("2009-01-01")
end_of_study_period   <- ymd("2021-12-31")

# PREGVAL 2009-2012----------------------------------------------------------
if (str_detect(table_name, "2009_2012") == TRUE){
  start_of_study_period <- ymd("2009-01-01")
  end_of_study_period <- ymd("2012-12-31")
}

if (str_detect(table_name, "2013_2017") == TRUE){
# PREGVAL 2013-2017----------------------------------------------------------
  start_of_study_period <- ymd("2013-01-01")
  end_of_study_period <- ymd("2017-12-31")
}

if (str_detect(table_name, "2018_2021") == TRUE){
# PREGVAL 2018-2021----------------------------------------------------------
  start_of_study_period <- ymd("2018-01-01")
  end_of_study_period <- ymd("2021-12-31")
}

```

```{r}
# load names-----------------------------------------------------------------
vid_names <- readRDS(file.path("..", "EHDEN", "Results", "vid_catalogue",
                               "vid_names.RDS"))

```

```{r}
# load population------------------------------------------------------------
# sips_clean <- readRDS(file.path("..", "PREGVAL", "Results", 
#                                 "sips", "sips_clean.RDS"))
# sips_total <- sips_clean

sips_total <- sips_empadronados


```

## Check variables

```{r}
# capture the names of the instance table------------------------------------
instance_names <- aed |> 
  names() 

```

The variables extracted from aed are: `r colorize(knitr::combine_words(instance_names), "blue")`.

```{r}
# check mandatory variables--------------------------------------------------
missing_mandatory_vars <- vid_names$aed_mandatory_names |> 
  keep(~. %nin% instance_names)

missing_mandatory_print <- "All mandatory vars are present"  

if (missing_mandatory_vars |> length() > 0) missing_mandatory_print <-
  glue("{knitr::combine_words(missing_mandatory_vars)} are missing")
      
color_mandatory_check <- if_else(missing_mandatory_vars |> length() > 0,
                                 "red", "green")

```

### Check mandatory vars 

`r colorize(missing_mandatory_print, color_mandatory_check)`.

```{r}
# check variables in full names----------------------------------------------
missing_full_vars <- vid_names$aed_all_names |> 
  keep(~. %nin% instance_names)

if(missing_full_vars |> length() > 0){
missing_full_print <- glue("{knitr::combine_words(missing_full_vars)} were not extracted")
}else{
missing_full_print <- "All possible vars are present"
}

color_full_check <- if_else(missing_full_vars |> length() > 0,
                                 "red", "green")

```

### Check all vars 

`r colorize(missing_full_print, color_full_check)`.

### Completeness

In @fig-aedcompleteness is shown the percentage of non-missing values for each variable. Non-mandatory variables are shown at the bottom of the figure.

```{r}
#| warning: false
# clean and fix aed----------------------------------------------------------
# manipulate unknown values to NA (0_00, -1, -2, etc.)
vector_of_nas <- c("", "0:00", "****", "0:DESCONOCIDA", "-1", "-2")

```


```{r}
# function to check completeness---------------------------------------------
check_completeness <- function(table, var){
if (as_string(ensym(var)) %nin% names(aed)) {
  return(lst(missing_obs = nrow(aed),
           complete_pct = 0,
           print_missing = "0%",
           color_missing = "red"
  ))
  }
total_obs <- table |> nrow() 
missing_obs <-  table |> filter(is.na({{var}})) |> nrow()
complete_pct <- 100 * ((total_obs - missing_obs)/total_obs) |> 
  round(3)
  
print_missing <- glue("{complete_pct}%")
color_missing <- if_else(missing_obs == 0, "green", "orange")
return(lst(missing_obs,
           complete_pct,
           print_missing,
           color_missing
            ))
}

```

```{r}
# apply the function to each var---------------------------------------------
miss_fecha_registro         <- check_completeness(aed, fecha_registro)
miss_fecha_alta            <- check_completeness(aed, fecha_alta)
miss_dpto_cod              <- check_completeness(aed, dpto_cod)
miss_centro_cod            <- check_completeness(aed, centro_cod)
miss_circ_alta_cod         <- check_completeness(aed, circ_alta_cod)
miss_circ_alta_desc        <- check_completeness(aed, circ_alta_desc)
miss_motivo_urg_cod        <- check_completeness(aed, motivo_urg_cod)
miss_motivo_urg_desc       <- check_completeness(aed, motivo_urg_desc)
miss_diag_cod              <- check_completeness(aed, diag_cod)
miss_diag2_cod             <- check_completeness(aed, diag2_cod)
miss_prioridad_cod         <- check_completeness(aed, prioridad_cod)
miss_tipo_codigo1          <- check_completeness(aed, tipo_codigo1)
miss_tipo_codigo2          <- check_completeness(aed, tipo_codigo2)

```

```{r}
# ensamble the missings------------------------------------------------------
tibble_missings <- data.frame(var = vid_names$aed_all_names,
                pct = map_dbl(vid_names$aed_all_names, 
                ~check_completeness(aed, var = !!sym(.x))$complete_pct),
                complete = map_chr(vid_names$aed_all_names, 
                ~check_completeness(aed, var = !!sym(.x))$print_missing)) |> 
  as_tibble() |> 
  mutate(var = fct_rev(fct_inorder(var))) |> 
  mutate(type = if_else(var %in% vid_names$aed_mandatory_names, 
                        "#9473d8", "#f2cce4"))

```

<br>

```{r}
#| label: fig-aedcompleteness
#| fig-cap: "Variables completeness"
# plot the missings----------------------------------------------------------

ggplot(tibble_missings, aes(y = var, x = pct)) +
  geom_col(aes(fill = type)) + 
  geom_text(aes(label = complete),
            colour = "black",
            position = position_nudge(7),
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Variable") +
  scale_x_continuous(name = "Completeness", 
                     breaks = c(0, 25, 50, 75, 100),
                     labels = scales::comma)
  
```

<br>

## Check content

```{r}
# total number of rows-------------------------------------------------------
total_aed_observations <- aed |> nrow()
  
```

The **aed** table has a total of **n = `r total_aed_observations |> pretty2()` observations**.

### Population

```{r}
# total distinct individuals-------------------------------------------------
distinct_sips_n <- aed |> distinct(sip) |> nrow() 
distinct_sips <- distinct_sips_n |> pretty2()
total_sips <- sips_total |> length() |> pretty2()
# individuals in population--------------------------------------------------
sips_in_pop_n <- aed |> 
  distinct(sip) |> 
  filter(sip %in% sips_total) |> 
  nrow() 
sips_in_pop <- sips_in_pop_n |> pretty2()

color_in_pop <- if_else(sips_in_pop < distinct_sips, "red", "green")

print_pop <- if_else(color_in_pop == "red", 
             glue("From these, there are {distinct_sips_n - sips_in_pop_n} individuals that are not included in the target population"),
             glue("All the individuals are included in the target population"))

percent_sips <- (sips_in_pop_n /  sips_total |> length()) * 100

print_percent_sips <- glue("{percent_sips |> round(2)}%")

```

- In **aed** table there are `r colorize(distinct_sips, "blue")` distinct individuals. `r colorize(print_pop, color_in_pop)`. Therefore, there are `r colorize(sips_in_pop, color_in_pop)` individuals included in the target population out of the `r colorize(total_sips, "purple")` total individuals in the cohort. These represents `r colorize(print_percent_sips, "blue")` of the total.

```{r}
# number of individuals per year---------------------------------------------
aed_sips_per_year <- aed |> 
  filter(sip %in% sips_total) |> 
  group_by(year = year(fecha_registro)) |> 
  distinct(sip) |> 
  count(year) |> 
  ungroup()

```

- The @tbl-sipsperyear shows the number of individuals per year of the study period.

<br>

```{r}
#| label: tbl-sipsperyear
#| tbl-cap-location: top
#| tbl-cap: "Number of individuals per year of calculation"
# create table of number of individuals per year-----------------------------
aed_sips_per_year |> 
  gt(id = "sipsperyear") |>  # need to name the table to apply CSS
  cols_label(year = "Year of admission",
             n = "Count of distinct individuals") |> 
  cols_align(
  align = c("center"),
  columns = everything()
  ) |> 
  tab_style(
    style = list(
      cell_fill(color = "#9473d8"),
      cell_text(color = "white", align = "center", weight = "bold")
    ),
    locations = cells_column_labels()) |> 
    opt_row_striping( row_striping = TRUE) |> 
  opt_css(
    css = "
    #sipsperyear tr:hover {
    background-color: #f2cce4;
    }
    ")

```

<br>

### Date of the admission

```{r}
# check if the date of the admission is inside the study period--------------
date_of_visit_print <- "All dates are inside the study period"  
color_of_visit_print <- "green"

n_visits_ok <- aed |> mutate(date_of_visit_ok = between(fecha_registro, 
                      start_of_study_period, end_of_study_period)) |> 
  summarise(n = 100 * mean(date_of_visit_ok, na.rm = TRUE)) |> 
  pull()

if (n_visits_ok < 100){

n_visits_before <- aed |> 
  mutate(date_of_visit_before = fecha_registro < start_of_study_period) |> 
  summarise(n = 100 * mean(date_of_visit_before, na.rm = TRUE)) |> 
  pull() |> round(2)

n_visits_after <- aed |> 
  mutate(date_of_visit_after = fecha_registro > end_of_study_period) |> 
  summarise(n = 100 * mean(date_of_visit_after, na.rm = TRUE)) |> 
  pull() |> round(2)

# n_visits_na <- aed |> mutate(date_of_visit_na = is.na(fecha_registro)) |> 
#   summarise(n = 100 * mean(date_of_visit_na)) |> pull()

date_of_visit_print <- glue("There are dates outside the study period. From the non-missing dates: \n
                            * **{n_visits_ok |> round(2)}%** are inside the study period. \n
                            * **{n_visits_before}%** occurred before the start of the study period. \n
                            * **{n_visits_after}%** occurred after the end of the study period") 
color_of_visit_print <- "red"
}      

min_date <- aed |> filter(!is.na(fecha_registro)) |>
  summarise(min(fecha_registro)) |> pull()
max_date <- aed |> filter(!is.na(fecha_registro)) |>
  summarise(max(fecha_registro)) |> pull()
  
```

The variable *fecha_registro* is missing in **`r miss_fecha_registro$missing_obs` observations**, so it is `r colorize(miss_fecha_registro$print_missing, miss_fecha_registro$color_missing)` complete. The minimum and maximum date are ***`r min_date`*** and ***`r max_date`*** respectively. @tbl-fechaing shows the number of admissions per year of *fecha_registro*.

`r colorize(date_of_visit_print, color_of_visit_print)`.

<br>

```{r}
#| label: tbl-fechaing
#| tbl-cap-location: top
#| tbl-cap: "Number of admissions each year of calculation"
# create table of number of admissions per year------------------------------
aed |> 
  count(year = year(fecha_registro)) |> 
  gt(id = "fechaing") |>  # need to name the table to apply CSS
  cols_label(year = "Year of the admission",
             n = "Count") |> 
  cols_align(
  align = c("left"),
  columns = everything()
  ) |> 
  tab_style(
    style = list(
      cell_fill(color = "#9473d8"),
      cell_text(color = "white", align = "left", weight = "bold")
    ),
    locations = cells_column_labels()) |> 
    opt_row_striping( row_striping = TRUE) |> 
  opt_css(
    css = "
    #fechaing tr:hover {
    background-color: #f2cce4;
    }
    ")

```

<br>

```{r}
# check month and year of fecha_registro-------------------------------------
aed_month_year_visit_date <- aed |> 
  count(month = month(fecha_registro, 
                      label = TRUE,
                      abbr = FALSE,
                      locale = "EN"), 
        year = year(fecha_registro),
        name = "n_month_year") |> 
  arrange(year, month)

aed_month_year_visit_date_min <- aed_month_year_visit_date |> 
  filter(n_month_year == min(n_month_year))
aed_month_year_visit_date_max <- aed_month_year_visit_date |> 
  filter(n_month_year == max(n_month_year))

print_month_year_visit_date_min <- glue(
  "{aed_month_year_visit_date_min |> pull(month)} {aed_month_year_visit_date_min |> pull(year)} with n = {aed_month_year_visit_date_min |> pull(n_month_year)}" )

print_month_year_visit_date_max <- glue(
  "{aed_month_year_visit_date_max |> pull(month)} {aed_month_year_visit_date_max |> pull(year)} with n = {aed_month_year_visit_date_max |> pull(n_month_year)}" )

```

The month and year with less admissions was `r colorize(print_month_year_visit_date_min, "blue")` and the month and year with more admissions was `r colorize(print_month_year_visit_date_max, "purple")`.

In @fig-aedingresoyear, @fig-aedingresomonth, and @fig-aedingresoday are presented the frequencies of years, months, and days of the admissions respectively.

<br>

```{r}
#| label: fig-aedingresoyear
#| fig-cap: "Admission year"
# plot year of fecha_registro------------------------------------------------
aed_year_visit <- aed |> 
  count(year_visit = year(fecha_registro), name = "n_year")

ggplot(aed_year_visit) +
  geom_col(aes(x = year_visit, y = n_year), fill = "#9473d8") +
  xlab("Admission year") +
  scale_y_continuous(name = "Count", labels = scales::comma) 

```

<br>

```{r}
#| label: fig-aedingresomonth
#| fig-cap: "Admission month"
# plot month of fecha_registro-----------------------------------------------
aed_month_visit <- aed |> 
  count(month_visit = month(fecha_registro, label = TRUE,
                                locale = "EN"), name = "n_month")

ggplot(aed_month_visit) +
  geom_col(aes(x = month_visit, y = n_month), fill = "#9473d8") +
  xlab("Admission month") +
  scale_y_continuous(name = "Count", labels = scales::comma) 

```

<br>

```{r}
#| label: fig-aedingresoday
#| fig-cap: "Admission day"
# plot day of fecha_registro-------------------------------------------------
aed_day_visit <- aed |> 
  count(day_visit = day(fecha_registro), name = "n_day")

ggplot(aed_day_visit) +
  geom_col(aes(x = day_visit, y = n_day), fill = "#9473d8") +
  scale_x_continuous(name = "Admission day", 
                   breaks = 1:31, labels = 1:31) +
  scale_y_continuous(name = "Count", labels = scales::comma) 

```

<br>



### Date of the discharge

```{r}
# check if the date of the visit is inside the study period------------------
date_of_visit_print <- "All dates are inside the study period"  
color_of_visit_print <- "green"

n_visits_ok <- aed |> mutate(date_of_visit_ok = between(fecha_alta, 
                      start_of_study_period, end_of_study_period)) |> 
  summarise(n = 100 * mean(date_of_visit_ok, na.rm = TRUE)) |> 
  pull()

if (n_visits_ok < 100){

n_visits_before <- aed |> 
  mutate(date_of_visit_before = fecha_alta < start_of_study_period) |> 
  summarise(n = 100 * mean(date_of_visit_before, na.rm = TRUE)) |> 
  pull() |> round(2)

n_visits_after <- aed |> 
  mutate(date_of_visit_after = fecha_alta > end_of_study_period) |> 
  summarise(n = 100 * mean(date_of_visit_after, na.rm = TRUE)) |> 
  pull() |> round(2)

# n_visits_na <- aed |> mutate(date_of_visit_na = is.na(fecha_alta)) |> 
#   summarise(n = 100 * mean(date_of_visit_na)) |> pull()

date_of_visit_print <- glue("There are dates outside the study period. From the non-missing dates: \n
                            * **{n_visits_ok |> round(2)}%** are inside the study period. \n
                            * **{n_visits_before}%** occurred before the start of the study period. \n
                            * **{n_visits_after}%** occurred after the end of the study period") 
color_of_visit_print <- "red"
}      

min_date <- aed |> filter(!is.na(fecha_alta)) |>
  summarise(min(fecha_alta)) |> pull()
max_date <- aed |> filter(!is.na(fecha_alta)) |>
  summarise(max(fecha_alta)) |> pull()

```

The variable *fecha_alta* is missing in **`r miss_fecha_alta$missing_obs` observations**, so it is `r colorize(miss_fecha_alta$print_missing, miss_fecha_alta$color_missing)` complete. The minimum and maximum date are ***`r min_date`*** and ***`r max_date`*** respectively. @tbl-fechaalta shows the number of discharges per year of *fecha_alta*.

`r colorize(date_of_visit_print, color_of_visit_print)`.

<br>

```{r}
#| label: tbl-fechaalta
#| tbl-cap-location: top
#| tbl-cap: "Number of discharges each year of calculation"
# create table of number of visits per year----------------------------------
aed |> 
  count(year = year(fecha_alta)) |> 
  gt(id = "fechaalta") |>  # need to name the table to apply CSS
  cols_label(year = "Year of the discharge",
             n = "Count") |> 
  cols_align(
  align = c("left"),
  columns = everything()
  ) |> 
  tab_style(
    style = list(
      cell_fill(color = "#9473d8"),
      cell_text(color = "white", align = "left", weight = "bold")
    ),
    locations = cells_column_labels()) |> 
    opt_row_striping( row_striping = TRUE) |> 
  opt_css(
    css = "
    #fechaalta tr:hover {
    background-color: #f2cce4;
    }
    ")

```

<br>

```{r}
# check month and year of fecha_alta-------------------------------------
aed_month_year_visit_date <- aed |> 
  count(month = month(fecha_alta, 
                      label = TRUE,
                      abbr = FALSE,
                      locale = "EN"), 
        year = year(fecha_alta),
        name = "n_month_year") |> 
  arrange(year, month)

aed_month_year_visit_date_min <- aed_month_year_visit_date |> 
  filter(n_month_year == min(n_month_year))
aed_month_year_visit_date_max <- aed_month_year_visit_date |> 
  filter(n_month_year == max(n_month_year))

print_month_year_visit_date_min <- glue(
  "{aed_month_year_visit_date_min |> pull(month)} {aed_month_year_visit_date_min |> pull(year)} with n = {aed_month_year_visit_date_min |> pull(n_month_year)}" )

print_month_year_visit_date_max <- glue(
  "{aed_month_year_visit_date_max |> pull(month)} {aed_month_year_visit_date_max |> pull(year)} with n = {aed_month_year_visit_date_max |> pull(n_month_year)}" )

```

The month and year with less discharges was `r colorize(print_month_year_visit_date_min, "blue")` and the month and year with more discharges was `r colorize(print_month_year_visit_date_max, "purple")`.

In @fig-aedaltayear, @fig-aedaltamonth, and @fig-aedaltaday are presented the frequencies of years, months, and days of the visits respectively.

<br>

```{r}
#| label: fig-aedaltayear
#| fig-cap: "Discharge year"
# plot year of fecha_alta------------------------------------------------
aed_year_visit <- aed |> 
  count(year_visit = year(fecha_alta), name = "n_year")

ggplot(aed_year_visit) +
  geom_col(aes(x = year_visit, y = n_year), fill = "#9473d8") +
  xlab("Discharge year") +
  scale_y_continuous(name = "Count", labels = scales::comma) 

```

<br>

```{r}
#| label: fig-aedaltamonth
#| fig-cap: "Discharge month"
# plot month of fecha_alta-----------------------------------------------
aed_month_visit <- aed |> 
  count(month_visit = month(fecha_alta, label = TRUE,
                                locale = "EN"), name = "n_month")

ggplot(aed_month_visit) +
  geom_col(aes(x = month_visit, y = n_month), fill = "#9473d8") +
  xlab("Discharge month") +
  scale_y_continuous(name = "Count", labels = scales::comma) 

```

<br>

```{r}
#| label: fig-aedaltaday
#| fig-cap: "Discharge day"
# plot day of fecha_alta-------------------------------------------------
aed_day_visit <- aed |> 
  count(day_visit = day(fecha_alta), name = "n_day")

ggplot(aed_day_visit) +
  geom_col(aes(x = day_visit, y = n_day), fill = "#9473d8") +
  scale_x_continuous(name = "Discharge day", 
                   breaks = 1:31, labels = 1:31) +
  scale_y_continuous(name = "Count", labels = scales::comma) 

```

<br>


### Visit service

The variable *motivo_urg_desc* is missing in **`r miss_motivo_urg_desc$missing_obs` observations**, so it is `r colorize(miss_motivo_urg_desc$print_missing, miss_motivo_urg_desc$color_missing)` complete. @tbl-visit shows all the services used in the primary care visits arranged by alphabetic order. @fig-aedserv shows the count of the utilization of each visit service. Finally, @fig-aedservyear shows the count of visits for the 10 most used services per year.

<br>

```{r}
#| label: tbl-visit
#| tbl-cap-location: top
#| tbl-cap: "Healths services used in the emergency deoartment visits"
# create table of motivo_urg_desc----------------------------------------------

aed |> 
  tabyl(motivo_urg_desc) |>
  adorn_pct_formatting(digits = 2) |> 
  gt(id = "serv") |>  # need to name the table to apply CSS
  cols_label(motivo_urg_desc = "Service",
             n = "Count",
             percent = "Percentage") |> 
  cols_align(
  align = c("left"),
  columns = everything()
  ) |> 
  tab_style(
    style = list(
      cell_fill(color = "#9473d8"),
      cell_text(color = "white", align = "left", weight = "bold")
    ),
    locations = cells_column_labels()) |> 
    opt_row_striping( row_striping = TRUE) |>
  tab_options(
    container.height = "700px"
  ) |>
  opt_css(
    css = "
    #serv tr:hover {
    background-color: #f2cce4;
    }
    ")

```

<br>

```{r}
#| label: fig-aedserv
#| fig-cap: "Primary care visit services"
# plot motivo_urg_desc-----------------------------------------------------------
x_pos <- nrow(aed) / 10

aed |>
  mutate(motivo_urg_desc = fct_lump_n(fct_infreq(motivo_urg_desc), n = 10, 
                                   other_level = "OTROS") |> fct_rev()) |> 
  count(motivo_urg_desc) |>
  mutate(n_all = sum(n)) |> 
  mutate(percent = glue("{round(100 * n / n_all, 1)}%")) |> 
  # make colour for na
  mutate(fill_color = if_else(is.na(motivo_urg_desc),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = motivo_urg_desc, x = n)) +
  geom_col(aes(fill = fill_color)) + 
  geom_text(aes(label = percent),
            colour = "black",
            size = 7,
            fontface = "bold",
            x = x_pos
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Health Service") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text = element_text(size = 20))

```

<br>

```{r}
#| label: fig-aedservyear
#| fig-cap: "Most used primary care visit services per year"
# plot motivo_urg_desc per year--------------------------------------------------

xpos2 <- x_pos/(aed |> distinct(year(fecha_registro)) |> nrow())

aed |>
  mutate(motivo_urg_desc = fct_lump_n(fct_infreq(motivo_urg_desc), n = 10, 
                                   other_level = "OTROS") |> fct_rev()) |>
  mutate(year = year(fecha_registro)) |>
  count(year, motivo_urg_desc) |>
  group_by(year) |> 
  mutate(n_year = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_year, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(motivo_urg_desc),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = motivo_urg_desc, x = n)) +
  geom_col(aes(fill = fill_color)) +
  facet_wrap(~year, ncol = 4) +
  geom_text(aes(label = percent),
            colour = "black",
            size = 7,
            fontface = "bold",
            x = xpos2
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Health Service") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(
    axis.text.y = element_text(size = 20),
    axis.text.x = element_text(size = 20, angle = 90))

```

<br>
 
### Diagnoses codes: diag_cod 

The variable *diag_cod* is missing in **`r miss_diag_cod$missing_obs` observations**, so it is `r colorize(miss_diag_cod$print_missing, miss_diag_cod$color_missing)` complete. @fig-aedcode1 shows the most employed diagnoses codes. Finally, @fig-aedcode1year shows the count of the 10 most employed codes per year.

<br>

```{r}
#| label: fig-aedcode1
#| fig-cap: "Diagnosis codes (diag_cod) used in specialist visits"
# plot diag_cod-----------------------------------------------------------
x_pos <- nrow(aed)/10

aed |>
  mutate(diag_cod = fct_lump_n(fct_infreq(diag_cod), n = 10, 
                                   other_level = "OTROS") |> fct_rev()) |>
  count(diag_cod) |> 
  mutate(n_all = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_all, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(diag_cod),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = diag_cod, x = n)) +
  geom_col(aes(fill = fill_color)) +
  geom_text(aes(label = percent),
            colour = "black",
            size = 7,
            x = x_pos,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Diagnosis codes") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text = element_text(size = 20))

```


<br>

```{r}
#| label: fig-aedcode1year
#| fig-cap: "Diagnosis codes (diag_cod) used in specialist visits per year"
# plot diag_cod per year-------------------------------------------------------

aed |>
  mutate(diag_cod = fct_lump_n(fct_infreq(diag_cod), n = 10, 
                                   other_level = "OTROS") |> fct_rev()) |>
  mutate(year = year(fecha_registro)) |>
  count(year, diag_cod) |>
  group_by(year) |> 
  mutate(n_year = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_year, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(diag_cod),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = diag_cod, x = n)) +
  geom_col(aes(fill = fill_color)) +
  facet_wrap(~year, ncol = 4) +
  geom_text_repel(aes(label = percent),
            colour = "black",
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Diagnosis Codes") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text.x = element_text(size = 20, angle = 90))

```

<br>

### Diagnoses codes: diag2_cod 

The variable *diag2_cod* is missing in **`r miss_diag2_cod$missing_obs` observations**, so it is `r colorize(miss_diag2_cod$print_missing, miss_diag2_cod$color_missing)` complete. @fig-aedcode1 shows the most employed diagnoses codes. Finally, @fig-aedcode1year shows the count of the 10 most employed codes per year.

<br>

```{r}
#| label: fig-aedcode2
#| fig-cap: "Diagnosis codes (diag2_cod) used in specialist visits"
# plot diag2_cod-----------------------------------------------------------
x_pos <- nrow(aed)/10

aed |>
  mutate(diag2_cod = fct_lump_n(fct_infreq(diag2_cod), n = 10, 
                                   other_level = "OTROS") |> fct_rev()) |>
  count(diag2_cod) |> 
  mutate(n_all = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_all, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(diag2_cod),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = diag2_cod, x = n)) +
  geom_col(aes(fill = fill_color)) +
  geom_text(aes(label = percent),
            colour = "black",
            size = 7,
            x = x_pos,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Diagnosis codes") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text = element_text(size = 20))

```


<br>

```{r}
#| label: fig-aedcode2year
#| fig-cap: "Diagnosis codes (diag2_cod) used in specialist visits per year"
# plot diag2_cod per year-------------------------------------------------------

aed |>
  mutate(diag2_cod = fct_lump_n(fct_infreq(diag2_cod), n = 10, ties.method = "first", 
                                   other_level = "OTROS") |> fct_rev()) |>
  mutate(year = year(fecha_registro)) |>
  count(year, diag2_cod) |>
  group_by(year) |> 
  mutate(n_year = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_year, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(diag2_cod),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = diag2_cod, x = n)) +
  geom_col(aes(fill = fill_color)) +
  facet_wrap(~year, ncol = 4) +
  geom_text_repel(aes(label = percent),
            colour = "black",
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Diagnosis Codes") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text.x = element_text(size = 20, angle = 90))

```

<br>

### Code vocabulary: tipo_codigo1

The variable *tipo_codigo1* is missing in **`r miss_tipo_codigo1$missing_obs` observations**, so it is `r colorize(miss_tipo_codigo1$print_missing, miss_tipo_codigo1$color_missing)` complete. @fig-aedtipo1 shows the count of the utilization of each visit service. Finally, @fig-aedtipo1year shows the count of visits for the 10 most used services per year.

<br>

```{r}
#| label: fig-aedtipo1
#| fig-cap: "Code (diag_cod) vocabularies used in specialist visits"
# plot tipo_codigo1----------------------------------------------------------
aed |>
  tabyl(tipo_codigo1) |>
  adorn_pct_formatting() |> 
  mutate(tipo_codigo1 = fct_reorder(tipo_codigo1, n)) |> 
  # make colour for na
  mutate(fill_color = if_else(is.na(tipo_codigo1),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = tipo_codigo1, x = n)) +
  geom_col(aes(fill = fill_color)) + 
  geom_text(aes(label = percent),
            colour = "black",
            position = position_nudge(100),
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Code Vocabulary") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text.y = element_text(size = 20))

```


<br>

```{r}
#| label: fig-aedtipo1year
#| fig-cap: "Code (diag_cod) vocabularies used in specialist visits per year"
# plot tipo_codigo1 per year--------------------------------------------------

aed |>
  mutate(tipo_codigo1 = fct_infreq(tipo_codigo1) |> fct_rev()) |>
  mutate(year = year(fecha_registro)) |>
  count(year, tipo_codigo1) |>
  group_by(year) |> 
  mutate(n_year = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_year, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(tipo_codigo1),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = tipo_codigo1, x = n)) +
  geom_col(aes(fill = fill_color)) +
  facet_wrap(~year, ncol = 4) +
  geom_text_repel(aes(label = percent),
            colour = "black",
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Code Vocabulary") +
  scale_x_continuous(name = "Count", labels = scales::label_comma()) +
  theme(axis.text.x = element_text(size = 20, angle = 90))

```

<br>

### Code vocabulary: tipo_codigo2

The variable *tipo_codigo2* is missing in **`r miss_tipo_codigo2$missing_obs` observations**, so it is `r colorize(miss_tipo_codigo2$print_missing, miss_tipo_codigo2$color_missing)` complete. @fig-aedtipo2 shows the count of the utilization of each visit service. Finally, @fig-aedtipo2year shows the count of visits for the 10 most used services per year.

<br>

```{r}
#| label: fig-aedtipo2
#| fig-cap: "Code (diag2_cod) vocabularies used in specialist visits"
# plot tipo_codigo2----------------------------------------------------------
aed |>
  tabyl(tipo_codigo2) |>
  adorn_pct_formatting() |> 
  mutate(tipo_codigo2 = fct_reorder(tipo_codigo2, n)) |> 
  # make colour for na
  mutate(fill_color = if_else(is.na(tipo_codigo2),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = tipo_codigo2, x = n)) +
  geom_col(aes(fill = fill_color)) + 
  geom_text(aes(label = percent),
            colour = "black",
            position = position_nudge(100),
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Code Vocabulary") +
  scale_x_continuous(name = "Count", labels = scales::comma) +
  theme(axis.text.y = element_text(size = 20))

```


<br>

```{r}
#| label: fig-aedtipo2year
#| fig-cap: "Code (diag2_cod) vocabularies used in specialist visits per year"
# plot tipo_codigo2 per year--------------------------------------------------

aed |>
  mutate(tipo_codigo2 = fct_infreq(tipo_codigo2) |> fct_rev()) |>
  mutate(year = year(fecha_registro)) |>
  count(year, tipo_codigo2) |>
  group_by(year) |> 
  mutate(n_year = sum(n)) |> 
  ungroup() |>
  mutate(percent = glue("{round(100 * n / n_year, 1)}%")) |> 
# make colour for na
  mutate(fill_color = if_else(is.na(tipo_codigo2),
                              "grey38", "#9473d8")) |>
ggplot(aes(y = tipo_codigo2, x = n)) +
  geom_col(aes(fill = fill_color)) +
  facet_wrap(~year, ncol = 4) +
  geom_text_repel(aes(label = percent),
            colour = "black",
            size = 7,
            fontface = "bold"
            ) +
  scale_fill_identity() +
  scale_y_discrete(name = "Code Vocabulary") +
  scale_x_continuous(name = "Count", labels = scales::label_comma()) +
  theme(axis.text.x = element_text(size = 20, angle = 90))

```

<br>

<div class="tocify-extend-page" data-unique="tocify-extend-page" style="height: 0;"></div>
